### 2021-08-15 doc/thesis/chapters/introduction.tex
adapt motivation

In the master's degree program Embedded Systems Design, a wide range of topics relate to digital signal processing, chip design and software development.
All of these disciplines find their application in an embedded system.
Multiple different methods of implementation are introduced for each topic and their usage is tested in practical sessions.
However, in the setting of a university course it is not always possible to look at the currently handled topic as a part of a larger, integrated system.
Instead, it is often treated as a standalone part that fulfills its own, specific functionality.
Therefore, one of the main motivation points for this thesis is to combine several disciplines and multiple implementation methods into a single system design, and treat it in this common project context.\\

@@

Since the development of an embedded system combines so many displines, it is of advantage to have knowledge of as many as possible of them.
However, not only understanding single parts, but to have an overview and understanding of the entire, integrated system and the interaction between those single parts is important in an embedded system.\\

>>>>

In the master's degree program Embedded Systems Design, a wide range of topics relate to digital signal processing, chip design and software development.
All of these disciplines find their application in an embedded system.
Multiple different methods of implementation are introduced for each topic and their usage is tested in practical sessions.
However, in the setting of a university course it is not always possible to look at the currently handled topic as a part of a larger, integrated system.
Instead, it is often treated as a standalone part that fulfills its own, specific functionality.
Therefore, one of the main motivation points for this thesis is to combine several disciplines and multiple implementation methods into a single system design, to find a universal workflow for design and verification, and treat them in this common project context.\\

@@

Since the development of an embedded system combines so many displines, it is of advantage to have knowledge of as many as possible of them.
However, not only understanding single parts, but to have an overview and understanding of the entire, integrated system and the interaction between those single parts is important in an embedded system.\\
%This further creates the motivation to find a solution for a universal design flow, that enables to combine the different implementation methods into a single system design.\\
